Figures and tables for paper

### 2021-10-18 analysis/04_figs-tables.Rmd
Prepped code for interaction contrasts

```{r crackdown-contrasts}
# Pull the posterior draws for government crackdown

@@

# Save plot
ggsave(
  "contrasts_hypothesis02.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

@@

@@

```{r issue-contrasts}
# Pull the posterior draws for issue area

@@

# Save plot
ggsave(
  "contrasts_hypothesis03.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```
> Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)

@@

@@

@@

```{r funding-contrasts}
# Pull the posterior draws for funding sources

@@

# Save plot
ggsave(
  "contrasts_hypothesis04.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```
> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor. Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]

@@

@@

@@

```{r practices-contrasts}

@@

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  accountibility = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

# Save plot
ggsave(
  "contrasts_hypothesis04.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```
> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]

@@

When comparing organizational practices, donors show an increased likelihood to donate to NGOs that are financially transparent as well as NGOs that are accountable and hold regular third party audits. Although financial transparency was hypothesized to increase donor's willingness to donate, we believed accountability practices would have an insignificant effect on influencing donor's willingness to donate; our analysis indicates that this is not the case.

@@

@@

@@

@@

@@

>>>>

# Hypothesis 2a, Relationship with Host Government

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown

@@

# Save plot
ggsave(
  "contrasts_hypothesis02a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

# Hypothesis 2b, Organization and Relationship with Host Government

@@

```{r crackdown-contrasts-b}

# Pull the posterior draws for organization*government crackdown interaction

# Reference Level = Friendly relationship with government
#  contrasts <- tibble(
#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
#    )

# Plot the contrasts
# contrasts %>%
#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
# ggsave(
#  "contrasts_hypothesis02b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
# )
```

@@

### Hypothesis 3, Issue Area

# Hypothesis 3a, Issue Area

> Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)

```{r issue-contrasts-a}
# Pull the posterior draws for issue area

@@

# Save plot
ggsave(
  "contrasts_hypothesis03a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

# Hypothesis 3b, Relationship with Host Government and Issue Area

@@

```{r issue-contrasts-b}

# Pull the posterior draws for government crackdown*issue area interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# contrasts <- tibble(
#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
# "contrasts_hypothesis03b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)
```

@@

# Hypothesis 4a, Funding Sources

> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor. Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources

@@

# Save plot
ggsave(
  "contrasts_hypothesis04a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```

@@

# Hypothesis 4b, Relationship with Host Government and Funding Sources

@@

```{r funding-contrasts-b}
# Pull the posterior draws for government crackdown*funding sources interaction

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
#contrasts <- tibble(
#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis04b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

```

# Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area

> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)

```{r funding-contrasts-c}
# Pull the posterior draws for funding sources*government crackdown*issue area interaction

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government
#contrasts <- tibble(
#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis04c.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

```

@@

# Hypothesis 5a, Organizational Practices

> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]

```{r practices-contrasts-a}

@@

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(financial_transparency, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```

Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.

# Hypothesis 5b, Organizational Practices

@@

```{r practices-contrasts-b}
# Pull the posterior draws for organizational practices

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```

Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent. However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.

# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources

@@

```{r practices-contrasts-c}
# Pull the posterior draws for government crackdown*organizational practices*funding sources interaction

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05c.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

```

@@

# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area

@@

```{r practices-contrasts-d}
# Pull the posterior draws for government crackdown*organizational practices*issue area interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05d.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

```

@@

# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources

@@

```{r practices-contrasts-e}
# Pull the posterior draws for government crackdown*organizational practices*issue area*funding sources interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# Reference Level = Funded primarily by many small private donations

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05e.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

```
